Model LF

### 2022-10-12 max_dp endogen stød.Rmd
Commit
Commmit

COMMENT> 
IDENTITY> prod
EQ> prod=prodk * (y/yk)
if> shock_prod_model <= 0
IDENTITY> prod
EQ> prod= prod_shock
if> shock_prod_model > 0
IDENTITY> prod
EQ> prod= prod_shock_sens
if> shock_prod_model > 0 & sens3_low >= 0

@@

nl_g_bs3 = Shock_bs3$simulation$nl_g

@@

rw_ds_03 = Shock_3$simulation$rw_ds
kuld_03 = Shock_3$simulation$shock_kuld

@@

```{r}
# Simulate the model (following shock)
Shock_5 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList5
                    )
```

@@

```{r}
###Gengivelse af stød til model
max_dp_sbs3_low = sens_3_bs_low$simulation$max_dp
wage_sbs3_low = sens_3_bs_low$simulation$wage
komp_r_sbs3_low = sens_3_bs_low$simulation$komp_r
part_sbs3_low = sens_3_bs_low$simulation$part
yk_ds_sbs3_low = sens_3_bs_low$simulation$yk_ds
pc_ds_sbs3_low = sens_3_bs_low$simulation$pc_ds
wage_ds_t_sbs3_low = sens_3_bs_low$simulation$wage_ds_t
pc_ds_sbs3_low = sens_3_bs_low$simulation$pc_ds
max_gap_sbs3_low = sens_3_bs_low$simulation$max_gap
wage_gap1_sbs3_low = sens_3_bs_low$simulation$wage_gap1
inflation_sbs3_low = sens_3_bs_low$simulation$inflation
wage_ds_sbs3_low = sens_3_bs_low$simulation$wage_ds

@@

inflation_s3_low = sens_3_S1_low$simulation$inflation

@@

```{r}
plot((prod_s3_low/prod_sbs3_low), col= "red", ylim= c(0.9, 1.1));
lines((prod_03/prod_bs3), col="black");
legend("top", legend=c("No suppression",
                       "Wage growth"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

>>>>

COMMENT> 
IDENTITY> prod
EQ> prod=prodk * (y/yk)
if> shock_prod_model <= 0
IDENTITY> prod
EQ> prod= prod_shock
if> shock_prod_model > 0
IDENTITY> prod
EQ> prod= prod_shock_sens
if> shock_prod_model > 0 & sens3_low > 0

@@

nl_g_bs3 = Shock_bs3$simulation$nl_g
inflation_bs3 = Shock_bs3$simulation$inflation

@@

rw_ds_03 = Shock_3$simulation$rw_ds
kuld_03 = Shock_3$simulation$shock_kuld
inflation_03 = Shock_3$simulation$inflation

@@

```{r}
# Simulate the model (following shock)
Shock_5 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList5
                    )

@@

```{r}
###Gengivelse af stød til model
max_dp_sbs3_low = sens_3_bs_low$simulation$max_dp
wage_sbs3_low = sens_3_bs_low$simulation$wage
komp_r_sbs3_low = sens_3_bs_low$simulation$komp_r
part_sbs3_low = sens_3_bs_low$simulation$part
yk_ds_sbs3_low = sens_3_bs_low$simulation$yk_ds
pc_ds_sbs3_low = sens_3_bs_low$simulation$pc_ds
wage_ds_t_sbs3_low = sens_3_bs_low$simulation$wage_ds_t
pc_ds_sbs3_low = sens_3_bs_low$simulation$pc_ds
max_gap_sbs3_low = sens_3_bs_low$simulation$max_gap
wage_gap1_sbs3_low = sens_3_bs_low$simulation$wage_gap1
inflation_sbs3_low = sens_3_bs_low$simulation$inflation
wage_ds_sbs3_low = sens_3_bs_low$simulation$wage_ds
emp_sbs3_low = sens_3_bs_low$simulation$emp

@@

inflation_s3_low = sens_3_S1_low$simulation$inflation
emp_s3_low = sens_3_S1_low$simulation$emp

@@

```{r}
plot((prod_s3_low/prod_sbs3_low), col= "red", ylim= c(0.9, 1.1), main= "Productivity");
lines((prod_03/prod_bs3), col="black");
legend("top", legend=c("Estimate set to 0.1",
                       "Estimate is 0.25"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot((inflation_s3_low-inflation_sbs3_low), col= "red", ylim= c(-0.0004, 0.0035));
lines((inflation_03-inflation_bs3), col="black");
legend("top", legend=c("Estimate set to 0.1",
                       "Estimate is 0.25"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

Udvikling i Employment med estimat = 0.1:

```{r}
plot((emp_s3_low-emp_sbs3_low)*1000, col= "red")
```
